%-------------------------
% Resume in Latex
% Author : Taimoor
%------------------------

\documentclass[a4,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{1pt}
\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    urlcolor=darkblue   % Set link color to dark blue
}

% Define dark blue color
\definecolor{darkblue}{RGB}{0, 0, 139}

% Adjust font
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%

\begin{document}

\begin{center}
    {\huge \scshape Muhammad Taimoor Aleem} \\ \vspace{10pt}
    \small
    \begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} c @{\extracolsep{\fill}} c @{\extracolsep{\fill}} c @{\extracolsep{\fill}} c}
      \faEnvelope\ \href{mailto:taimooraleem01@gmail.com}{\underline{taimooraleem01@gmail.com}} &
      \faLinkedin\ \href{https://linkedin.com/in/TaimoorAleem}{\underline{/TaimoorAleem}} &
      \faGithub\ \href{https://github.com/TaimoorAleem}{\underline{/TaimoorAleem}} &
      \faGlobe\ \href{https://taimooraleem.com}{\underline{taimooraleem.com}} &
      \faPhone\ (416) 827 0507
    \end{tabular*}
\end{center}
\vspace{-18pt}

%-----------SUMMARY-----------
\section{Summary}
\vspace{3pt}
\begin{itemize}[noitemsep, nolistsep]
    \item Highly motivated 4th Year Computer Science student with a strong passion for Software Development and AI.
    \item Proven record of leveraging technical and interpersonal skills to excel in internships \& extracurricular roles.
\end{itemize}
\vspace{-10pt}

%-----------SKILLS-----------
\section{Skills}
    \begin{center}
        \begin{tabular}{@{\hspace{0em}} r @{\hspace{1.2em}} p{0.70\textwidth} @{}}
                {\textbf{Programming Languages}}    &   C\#, SQL, Python, JavaScript, TypeScript, Java, C/C++, \textrm{\LaTeX}\\
              {\textbf{Tools \& Technologies}}    &   .NET, ASP.NET Core (MVC / Web API), React.js, Next.js, Express.js, Node.js, Flask, Bootstrap, Linux, SQL Server, SQLite, MongoDB, Google Firestore\\
        \end{tabular}
    \end{center}
\vspace{-26pt}

%-----------EXPERIENCE-----------
\section{Experience}
\vspace{-4pt}
       \resumeSubHeadingListStart
       
           \resumeProjectHeading
            {\textbf{Software Developer Intern} $|$ \footnotesize{Dayforce - Wallet Feature Team}}{Jan 2025 - Dec 2025 (12 Months)}
            \vspace{-16pt}
            \resumeItemListStart
                \resumeItem{Developing and maintaining APIs in C\# / .NET, utilizing Entity Framework Core and SQL Server on Azure to enable seamless digital wallet integrations, and collaborating with cross-functional teams in an Agile environment.}
            \resumeItemListEnd
            \vspace{-18pt}
            
            \resumeProjectHeading
            {\textbf{Software Developer} $|$ \footnotesize{Skill Squirrel} $|$ \href{https://drive.google.com/file/d/16khUcRUuoAtqCSfgY1nGbZEthy-r0ZdX/view?usp=sharing}{\underline{Work Term Evaluation} \faExternalLink}}{May 2024 - Nov 2024 (7 Months)}
            \vspace{-16pt}
            \resumeItemListStart
                \resumeItem{Successfully developed a working prototype that incorporates Generative AI and prompt-engineering using Python and Microsoft Azure OpenAI API Service for a feature that aims to enhance user experience and product functionality.}
            \resumeItemListEnd
    
    \resumeSubHeadingListEnd
\vspace{-20pt}

%-----------EXTRA-CURRICULAR-----------
\section{Extra-Curricular Experience \& Awards}
\vspace{-2pt}
       \resumeSubHeadingListStart
       
        \resumeProjectHeading
        {\textbf{Technology Lead \& Sponsorship Team Member} $|$ \footnotesize{Sheridan Hackville Club}}{Mar 2024 - Jan 2025}
        \vspace{-16pt}
        \resumeItemListStart
            \resumeItem{Contributed to development of the website of the \href{https://hackville.io}{\underline{Hackville 2025}} hackathon event by utilizing Webflow and collaborating with the design team, ensuring its readiness for use by 300+ applicants.}
            \resumeItem{Successfully secured Google to sponsor our event with over \$700 CAD. Collaborated with the GDG Sheridan Club to plan a workshop and craft the "Best Use of Google Cloud" prize track for our participants.}
        \resumeItemListEnd
        \vspace{-18pt}

        \resumeProjectHeading
        {\textbf{Workshop Organizer} $|$ \footnotesize{Google Developer Student Club}}{Sep 2024 - Jan 2025}
        \vspace{-16pt}
        \resumeItemListStart
            \resumeItem{Organized an introductory Machine Learning workshop at Hackville 2025 by appointing speakers, preparing the content and collaborating with the Design Lead to prepare the presentation slides.}
        \resumeItemListEnd
        \vspace{-18pt}
        
        \resumeProjectHeading
        {\textbf{Best UI Design Award} $|$ \footnotesize{Hackville 2024} $|$ \href{https://devpost.com/software/buddyfinder-c0rak1}{\underline{Devpost Link} \faExternalLink}}{Jan 2024}
        \vspace{-16pt}
        \resumeItemListStart
            \resumeItem{Single-handedly developed the front-end of a project to achieve the Best UI Design Award at Hackville 2024 hackathon.}
        \resumeItemListEnd
    
    \resumeSubHeadingListEnd
\vspace{-20pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \vspace{-2pt}
    
        \resumeProjectHeading
          {\textbf{\href{https://github.com/TaimoorAleem/DollarSenseApp}{\underline{Dollar Sense} \faExternalLink}} $|$ \emph{Flask, Python, Scikit-Learn, React.js, TypeScript} $|$ Academic}{Apr 2024}
          \resumeItemListStart
            \resumeItem{Contributed to the development of a full-stack personal budget tracker website by developing a dynamic dashboard with React.js and Flask, utilizing RESTful APIs to process and display data in real-time.}
            \resumeItem{Implemented a machine learning model with scikit-learn to predict monthly expenses from transaction data, improving financial planning accuracy for users by analyzing historical spending patterns.}
          \resumeItemListEnd
          \vspace{-16pt}

        \resumeProjectHeading
          {\textbf{\href{https://github.com/TaimoorAleem/FinShare}{\underline{FinShare} \faExternalLink}} $|$ \emph{ASP.NET Core Web API, C\#, SQL Server} $|$ Personal}{Aug 2024}
          \resumeItemListStart
            \resumeItem{Developed a backend-only application using ASP.NET Core Web API, to manage stock portfolios and user comments, implementing RESTful APIs, JWT authentication, and entity relationships.}
            \resumeItem{Utilized Entity Framework Core, asynchronous programming, and repository pattern to ensure efficient database interactions, dynamic sorting, and filtering, enhancing overall application performance and maintainability}
          \resumeItemListEnd
          \vspace{-16pt}

        \resumeProjectHeading
          {\textbf{AI Cricket Coach (Capstone Project)} $|$ \emph{Python, OpenCV, Google Cloud, Flutter} $|$ Academic}{Sep 2024 - Apr 2025}
          \resumeItemListStart
            \resumeItem{Serving as the project leader to develop a mobile application that utilizes OpenCV to track the ball trajectory and Machine Learning to provide personalized feedback to athletes during training.}
            \resumeItem{Following the complete SDLC including documentation, design, and testing; implemented Clean Archietcture for the Flutter mobile app and incorporated Google Cloud services like Cloud Run \& Firestore for storage and processing.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-20pt}

%-----------EDUCATION-----------
\section{Education}
\vspace{2pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Honours Bachelor of Computer Science ( Specialization in Data Analytics )}{Sep 2021 -- Apr 2026}
      {Sheridan College}{Oakville, ON}
      \vspace{8pt}
      
  \resumeSubHeadingListEnd
\vspace{-50pt}

\end{document}
